---
title: "Data Visualization Gallery"
author: "Jubayer Hossain"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
---

```{r setup, include=FALSE}
library(ggplot2)
library(plotly)
library(plyr)
library(flexdashboard)
```


Distribution
=======================================================================

Row 
-----------------------------------------------------------------------

### Histogram 

```{r, echo=TRUE, fig.align="left"}
plot(iris$Sepal.Length, iris$Sepal.Width)
``` 

### geom_smooth Linear Regression



Row
-----------------------------------------------------------------------

### geom_smooth with Loess Smoothed Fit



### Constraining Slope with stat_smooth



Correlation
=======================================================================

Row
-----------------------------------------------------------------------

### stat_density Example



### Add Conditional Density Curves to Plot


Row
-----------------------------------------------------------------------

### geom_density and facet_wrap Together


### Density and Scatterplot Overlay Using geom_density


Ranking
=======================================================================



Evolution
=======================================================================



Maps
=======================================================================


About
======================================================================= 
Welcome to Data Visualization Gellery. I am Jubayer, recent alumni with Bachelor and Master’s in Microbiology. I am the founder of CHIRAL Bangladesh, a non-profit organization dedicated to health research to improve lives in Bangladesh. I aspire to maximize the quality of life of the human around me by working at the intersection of education, technology, and health research.

This is a short sequence of notes on data visualization, data manipulation, data cleaning, specially in the field of data science written by [Jubayer Hossian](https://jhossain.com/). 

